---
title: "Human Resources"
output:
  html_document:
    df_print: paged
---

```{r,include=FALSE}
# Load my libraries
source('library.R')
```

# Summary

This is an analysis of the *Human Resources Analytics* dataset on Kaggle.
The goal is analyze employee attrition or churn or employee turn over.  

## File descriptions

*    HR_train.csv - the training set
*    HR_test.csv - the test set
*    HR_sample_submission.csv - a sample submission file in the correct format

## Data fields

*    empID: employee ID
*    satisfaction_level
*    last_evaluation
*    number_project
*    average_montly_hours
*    time_spend_company: time spent at the company
*    Work_accident: whether they have had a work accident (0, 1)
*    promotion_last_5years: whether they have had a promotion in the last 5 years (0, 1)
*    department
*    salary
*    left: whether the employee has left (0, 1)

# Data Description

Read the data.
```{r}
d <- read_csv(file.path('data','HR_comma_sep.csv'))
```

Look a the first few lines.
```{r}
head(d)
```

Plots and tables of the data.
Look for a pattern to explain why people leave.  

```{r}
d %>% ggplot(x=aes(as.character(number_project),y=satisfaction_level,color=as.character(left))) + 
  geom_boxplot(aes(as.character(number_project),y=satisfaction_level,color=as.character(left)))
```


## Fit a model
Use glm and the binomial family to model the probability of a person leaving.

```{r}
model_1 <- glm(left ~ number_project, data=d, family = 'binomial')
```

```{r}
model_1 %>% broom::glance()
```
```{r}
model_1 %>% broom::tidy()
```
```{r}
model_2 <- glm(left ~ ., data=d, family = 'binomial')
```

```{r}
model_2 %>% broom::tidy()
```

```{r}
library(dbplyr)
```

```{r}
d %>% ggplot() +
  geom_boxplot(aes(x=satisfaction_level,y=left,group=left) )
```



```{r}
d_3 <- d %>% dplyr::select(left,satisfaction_level,last_evaluation,number_project,average_montly_hours,time_spend_company,Work_accident,promotion_last_5years)  
```

```{r}
summary(d_3)
```


```{r}
model_3 <- glm(left ~ ., data=d_3, family = 'binomial')
```

```{r}
names(model_3)
```


```{r}
model_3 %>% broom::tidy()
```
```{r}
d_3 <- model_3 %>% broom::augment(type.predict='response')
```
```{r}
d_3 <- d_3 %>% mutate( left_p = .fitted > .5)
```

```{r}
d_3 %>% group_by(left) %>% summarise(n())
```


```{r}
d_3 %>% group_by(left_p) %>% summarise(n())

```
```{r}
d_3 %>% group_by(left_p,left) %>% summarise(n())
```





```{r}
d_3 %>% ggplot(aes(.fitted)) + geom_density()
```



```{r}
d2 <- model_3 %>% broom::augment(type='response') 
```

```{r}
names(d2)
```


```{r}
d2 %>%  mutate(left_predicted = exp(.fitted))
```











```{r}
```


## Extract model results
Use package broom to extract the results.  

## Interpret the results
The model will predict the probability of a person leaving.

```{r}

```









# R Resources on the Web

These pages on the web provide examples of methods used in this analysis.

* [Kaggle Human Resources Analytics][Human Resources Analytics]
* [Interactive Documents][Interactive Documents]
* [Data Visualization with ggplot2][ggplot2 cheat]
* [R Markdown][R Markdown]
* [modelr on githum][modelr gh]
* [tidyr on github][tidyr gh]
* [tidyr][tidyr]
* [Data Wrangling in R: tidyr][Data Wrangling]
* [broom intro][broom intro]
* [broom vignette][broom vignette]
* [Plotting logistic regression][plotting logistic regression]
* [Interactive Documents][Interactive Documents]
* [Interactive Web Apps with Shiny Cheat Sheet][shiny cheat]
* [This github repository][data_mining]



# References

[Human Resources Analytics]: https://www.kaggle.com/c/sm/data 
[tidyr gh]: https://github.com/tidyverse/tidyr/blob/master/man/expand.Rd
[tidyr]: http://tidyr.tidyverse.org/reference/expand.html
[modelr gh]: https://github.com/tidyverse/modelr/blob/master/R/predictions.R
[ggplot2 cheat]: https://www.rstudio.com/wp-content/uploads/2016/11/ggplot2-cheatsheet-2.1.pdf
[R Markdown]: http://rmarkdown.rstudio.com/authoring_basics.html]
[Interactive Documents]: http://rmarkdown.rstudio.com/authoring_shiny.html
[Data Wrangling]: http://clayford.github.io/dwir/dwr_11_tidyr.html
[broom intro]: http://varianceexplained.org/r/broom-intro/
[broom vignette]: https://cran.r-project.org/web/packages/broom/vignettes/broom.html
[plotting logistic regression]: https://blogs.uoregon.edu/rclub/2016/04/05/plotting-your-logistic-regression-models/
[Interactive Documents]: http://rmarkdown.rstudio.com/authoring_shiny.html
[shiny cheat]: http://shiny.rstudio.com/images/shiny-cheatsheet.pdf
[data_mining]: git@github.com:harlananelson/data_mining.git


