---
title: "Tables"
output:
  html_document:
    df_print: paged
---
Keep a list of packages used in the R script called `library`.
```{r,include=FALSE}
# Load my libraries
source('library.R')
```
Read the data.  Note: the data must be in a `data` sub directory of your project directory
```{r}
d <- read_csv(file.path('data','HR_comma_sep.csv'))
```
```{r}
d <- d %>% mutate(left_f = factor(left,levels=c(0,1),labels=c('No','Yes')))
```


# Create two way tables of categorical variables.

First, get a list of the fields
```{r}
sapply(d,"class")
```
Create a tabulation
```{r}
tab <- d %$% table(left_f,number_project)
print(tab)
```
Calculate a chisquared measure of association.
You can see that of  the people who left, 43.9% has only two projects and most of the people who
stayed had 3 or 4 projects.
```{r}
d %$% CrossTable(left_f,number_project,chisq=TRUE,prop.r=TRUE,prop.c = FALSE,expected=FALSE)
```
Create some plots of the table. 
The bars are above zero if there are more observations than expected and below zero if there or less
```{r}
assoc(tab)
```

```{r}
mosaic(tab)
```

```{r}
plot(tab)
```






